---
title: "datasauRus"
author: "Kasia Banas"
date: "2024-09-26"
output: html_document
---

Install and load the datasauRus library:

```{r}
# install.packages("datasauRus")
library(datasauRus)
```

Load the tidyverse: 
```{r}
library(tidyverse)
```

`datasaurus_dozen` is a dataset demonstrating the utility of visualization. 
These 12 datasets are equal in standard measures: mean, standard deviation, 
and Pearson's correlation. But they look very different
Run the chunk below to get more info about this dataset:

```{r}
?datasaurus_dozen
View(datasaurus_dozen)
```

See what datasets are in the datasaurus_dozen:

```{r}
datasaurus_dozen %>% 
  distinct(dataset)
```

## Exercise 1
Pick 2 datasets and plot them next to one another
(I'd recommend scatterplot, use facets if you like)
```{r}
plot1 <- datasaurus_dozen %>%
  filter(dataset == "dino" | dataset == "star")
plot1 %>%
  ggplot(aes(x= x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(facets = ~ dataset)
```

## Exercise 2
For these same two datasets, find the mean and standard deviation
for the x and y variable in each. What did you find? 
```{r}
vlines <- lines %>%
  filter(dataset == "v_lines") 
summary(vlines)
hlines <- lines %>%
  filter(dataset == "h_lines")
summary(hlines)
sd(vlines$x)
sd(vlines$y)
sd(hlines$x)
sd(hlines$y)

#
datasaurus_dozen %>%
  filter(dataset == "dina" | dataset == "star")
  group_by(dataset) %>%
  summarise(mean_x = mean(x), sd_x = (sd(x)), mean_y = mean(y), sd_y = sd(y))

#they all have same mean and sd plots are not necessarily same so always plot ahead 

```